---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rsa.helpr

<!-- badges: start -->
[![R-CMD-check](https://github.com/rtaylor456new/rsa.helpr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/rtaylor456new/rsa.helpr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->


The goal of rsa.helpr is to enhance efficiency, accessibility, and reproducibility in vocational rehabilitation (VR) analysis. Specifically, the focus is to streamline the cleaning and analysis of RSA-911 and Transition Readiness Toolkit (TRT) data, a new measure of program effectiveness.

## Installation

You can install the development version of rsa.helpr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rtaylor456new/rsa.helpr")
```

## Example

This is simply an example of loading the package and examining function 
documentation.

```{r example}
library(rsa.helpr)
# ?load_data
# ?clean_utah
# ?clean_scores
# ?create_metadata
# ?visualize_densities
```


For detailed information and demonstration of `rsa.helpr` in action, see the 
vignette "rsa.helpr.Rmd".

